Regular singular Volterra equations on complex domains

### 2023-08-13 reg-sing-volterra.tex
Draft overview of main result proofs

As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$. Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}$ that contains all functions of exponential type. Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined
\subsubsection{Bounds near $\zeta = 0$}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.

Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$. However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin. Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
\begin{align*}
|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
&\leq \frac{\tau}{|\zeta(a)|} + C \\
&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
&\le \frac{\tau + C\delta}{|\zeta(a)|}
\end{align*}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.
\textcolor{orange}{[\ldots]}

\color{RoyalBlue}
On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by keeping $a,a'$ close enough to $\zeta=0$. If we choose $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
\begin{align*}
|\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)}\right\vert +\frac{\tau}{|\zeta(a)|}\\
&\leq \varepsilon +\frac{\tau}{|\zeta(a)|}.
\end{align*}
\textcolor{magenta}{[Condition~\eqref{cond:sing} doesn't say that for every $\varepsilon > 0$, this bound holds for small enough $\delta > 0$. It only says that when $\delta > 0$ is small enough, the bound holds for some $\varepsilon$]}
\color{black}

@@

 \color{Tomato}

 Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]

Then,

\begin{align*}
    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
    &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
\end{align*}

The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small. We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

@@

\color{Tomato}
\begin{align*}
    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like

with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.

\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely

\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]

with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}

\begin{verify}
    \begin{align*}
        \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
        &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
        &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
    \end{align*}
\end{verify}
\color{black}

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}). By choosing a small enough positive radius $R$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$. Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.

@@

Let's set $\Lambda > \lambda_\Delta$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge R$ for these points:
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R(1 - t)}\;dt. \]

We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$. To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration separately. At the beginning---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
\begin{align*}
\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2} \lambda_\Delta)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\textcolor{orange}{2} \lambda_\Delta)R} \int_0^{1/5} t^{\rho-1}\;dt \\
& = e^{-\frac{4}{5}(\Lambda \textcolor{orange}{2} \lambda_\Delta)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
\end{align*}
At the end, we instead use a worst-case estimate on $t^{1-\rho}$:
\begin{align*}
\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda -\textcolor{orange}{2} \lambda_\Delta)R(1 - t)}\;dt \\
& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R} \right] \\
& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R}.
\end{align*}

We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 R^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$. Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter. Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.

>>>>

As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$. Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type. Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
In this section, we'll prove the results stated in Section~\ref{sec:results}. Our arguments will follow the process of solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by Picard iteration.

The prototype solution $\solproto$ is our initial guess. When we apply $\volterra = \hardpart + \softpart$ to it, the singular part $\hardpart$ leaves it unchanged, as we'll show in Section~\ref{sec:construction}. We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.

To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$. In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\Omega)$. The perturbed operator $\volterra$ therefore sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$.

When we apply $\volterra$ again, it contracts the perturbation term in $\singexpalg{\tau-1+\epsilon}(\domain)$. More precisely, by making $\Lambda$ large enough, we can ensure that the subspace $\singexp{\tau+1+\epsilon}{\Lambda}(\domain)$ both contains the perturbation term and is contracted by $\volterra$. We'll prove this in Section~\ref{sec:V is a contraction}.

We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$. The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.

%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations

%%To see what the perturbation $\softpart$ does to $\solproto$, we first show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\Omega)$. We then show in Section~\ref{sec:image under soft_part} that $\softpart$ has the

%%The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$. In this section, we prove the results, showing that our solution method works as expected.

%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}. We start by constructing the {\em prototype solution} $\solproto$ of the simpler equation $\solwhole = \hardpart \solwhole$, which has essentially the same singularity.

%%The plan starts with the explicit

%%The first step of the plan is to construct the {\em prototype solution} $\solproto$, which satisfies the simpler equation $\solwhole = \hardpart \solwhole$. In Section~\ref{sec:proto-construction-regularity}, we

%%with the ultimate goal of proving Theorem~\ref{thm:general_volterra}. This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by first constructing the {\em prototype solution} $\solproto$, which explicitly describes what's going on near the singularity, and then adding a less singular perturbation $\solptb$.

%%the explicit {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ can be perturbed uniquely

%%when we perturb the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ to the more general equation $\solwhole = \volterra \solwhole$, the prototype solution $\solproto$ gets perturbed

%%the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where the {\em prototype solution} $\solproto$ captures

%%This equation says that once we have the {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$, we can

%%This theorem says that if we start with a certain explicit solution $\solproto$ of the equation $\solwhole = \hardpart \solwhole$,

%%This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by splitting $\volterra$ into the singular part $\hardpart$ and the perturbation $\softpart$,

%%constructing an explicit {\em prototype solution} of the equation $\solwhole = \hardpart \solwhole$

%%This theorem says that for a perturbed Volterra operator $\volterra = \hardpart + \softpart$ of the kind described in Section~\ref{setting}, the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where $\solproto = \hardpart \solproto$ and $\solptb$ is a less singular perturbation.
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined
\subsubsection{Bounds near $\zeta = 0$}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.

Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$. However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin. Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
\begin{align*}
|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
&\leq \frac{\tau}{|\zeta(a)|} + C \\
&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
&\le \frac{\tau + C\delta}{|\zeta(a)|}
\end{align*}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.

@@

% \color{Tomato}

 %Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

%\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]

%Then,

%\begin{align*}
 %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
 %   &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
  %  &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
   % &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
%\end{align*}

%The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small. We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

@@

%\color{Tomato}
%\begin{align*}
 %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
  %  &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
   % &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
%\end{align*}
%Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like

%\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]

%We deduce that

%\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]

%with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.

%\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely

%\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]

%with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}

%\begin{verify}
 %   \begin{align*}
  %      \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
   %     &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
    %    &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
    %\end{align*}
%\end{verify}
%\color{black}

@@

\begin{prop}\label{prop:get-contraction}
Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
\end{prop}
\begin{rmk}
For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
\end{rmk}
First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
\begin{equation}\label{near-limit}
|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
\end{equation}
for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}). By choosing a small enough positive radius $\textcolor{orange}{\delta}$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$. Complementarily, let $\far$ be the part of $\domain$ where $\textcolor{orange}{\delta} \le |\zeta|$.

@@

Let's set $\Lambda > \lambda_\Delta$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \textcolor{orange}{\delta}$ for these points:
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt. \]

We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$. To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration separately. At the beginning---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
\begin{align*}
\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}} \int_0^{1/5} t^{\rho-1}\;dt \\
& = e^{-\frac{4}{5}(\Lambda \textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
\end{align*}
At the end, we instead use a worst-case estimate on $t^{1-\rho}$:
\begin{align*}
\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda -\textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt \\
& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}} \right] \\
& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}}.
\end{align*}

We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 \textcolor{orange}{\delta}^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$. Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter. Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
